Sparse Function-space Representation \\ of Neural Networks

### 2023-05-14 paper/main.tex
rewrite 2.1

A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate such as the Laplace-GNN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}. The Laplace GNN takes the MAP solution and approximates the Hessian of our loss function  $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the GGN approximation. Another way of viewing the

@@

\begin{equation} 
	\valpha_{\vu}  =  \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}, \quad
	\vbeta_{\vu} =  \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
\label{eq:dual_sparse}
\end{equation}
Using the sparse definition of the dual variables our sparse GP posterior takes the following form:
\begin{equation}\label{eq:dual_sparse_post}
   \myexpect_{q_{\vu}(\vf)}[\vf_i] = \vkzs^{\T} \MKzz^{-1}   \valpha_{\vu} , \quad 
   \textrm{Var}_{q_{\vu}(\vf)}[\vf_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
\end{equation}
where $\MKzz$ and $\vkzs$ are define similarly to $\MKxx$ and $\vk_{\vx i}$ but now over the $\MZ \in \R^{M \times D} $ inducing points instead of the full dataset $\MX$. The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ and a kernel function $\kappa$. Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred} we can see that the computational complexity is now $\mathcal{O}(m^3)$ to $\mathcal{O}(n^3)$ where $m \ll n$.  Crucially given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact form of the full model projected using the kernel. Our approach contrasts to \citet{immerImprovingPredictionsBayesian2021}, which uses a subset of the full model, a less principled approach to build a sparse model given it ignores the information in the dataset. It is important to highlight that the sparsifying approach is independent of the approximate inference technique. The \cref{eq:dual_param} are determined from the neural network. More complicated inference techniques, such as variational inference, could be used, but given its simplicity, we only need a trained neural network; we use a Laplace approximation in our experiments.

@@

 \end{tikzpicture}}
 \end{subfigure}
 \hfill
  \setlength{\figurewidth}{.4\textwidth}
  \setlength{\figureheight}{\figurewidth}
 \begin{subfigure}{.78\textwidth}
   % \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
   % \includegraphics[width=0.5\textwidth]{./fig/rl.pdf}
   \input{./fig/rl.tex}
 \end{subfigure}
 \hfill
 \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
 \label{fig:rl}
\end{figure}

>>>>

A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate such as the Laplace-GNN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}. The Laplace GNN takes the MAP solution and approximates the Hessian of our loss function  $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the GGN approximation. Another way of viewing the approximation is that we build the following approximate model $\hat{f}_\weights(\mathbf{x}_{i}) = \Jac{\weights}{\mathbf{x}_i} \vw $  where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian. Using such an approximation we arrive at the Laplace-GGN posterior $q(\vw;  f_{\vw^*}(\vx_i) )$

@@

\begin{equation} 
	\valpha_{\vu}  =  \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}, \quad
	\vbeta_{\vu} =  \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
\label{eq:dual_sparse}
\end{equation}
Using the sparse definition of the dual variables our sparse GP posterior takes the following form:
\begin{equation}\label{eq:dual_sparse_post}
   \myexpect_{q_{\vu}(\vf)}[f_i] = \vkzs^{\T} \MKzz^{-1}   \valpha_{\vu} , \quad 
   \textrm{Var}_{q_{\vu}(\vf)}[f_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
\end{equation}
where $\MKzz$ and $\vkzs$ are define similarly to $\MKxx$ and $\vk_{\vx i}$ but now over the $\MZ \in \R^{M \times D} $ inducing points instead of the full dataset $\MX$. The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ and a kernel function $\kappa$. Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred} we can see that the computational complexity is now $\mathcal{O}(m^3)$ to $\mathcal{O}(n^3)$ where $m \ll n$.  Crucially given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact form of the full model projected using the kernel. Our approach contrasts to \citet{immerImprovingPredictionsBayesian2021}, which uses a subset of the full model, a less principled approach to build a sparse model given it ignores the information in the dataset. It is important to highlight that the sparsifying approach is independent of the approximate inference technique. The \cref{eq:dual_param} are determined from the neural network. More complicated inference techniques, such as variational inference, could be used, but given its simplicity, we only need a trained neural network; we use a Laplace approximation in our experiments.

@@

 \end{tikzpicture}}
 \end{subfigure}
 \hfill
 \begin{subfigure}{.78\textwidth}
   \centering\scriptsize
   \setlength{\figurewidth}{\textwidth}
   \setlength{\figureheight}{.5\figurewidth}
   \pgfplotsset{axis on top}
   \input{./fig/rl.tex}
 \end{subfigure}
 \hfill
 \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
 \label{fig:rl}
\end{figure}
